---
title: "Weight of Fish"
author: "Janette Quezada"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
```


## import fish CSV using the import function that Luz found


# Predicting Fish Weight



## Perch

```{r}
Fish= read.csv('Fish.csv')
Perch = filter (Fish,Species == 'Perch')
Perch=subset(Perch,select=-Species)
weightPerch = lm(Weight~Length1 + Length2 +Length3 + Height + Width, data = Perch)  
summary.lm(weightPerch)
``` 
The adjusted r square for perch is 0.9372.


### Best Models

### Best Two regressor model



```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```                                                                                                                                                                                                                            




The best one variable is height. The best 2 variable predictor is height and width. 






 
## Pike

```{r}
Pike = filter (Fish,Species == 'Pike')
Pike=subset(Pike,select=-Species)
weightPike = lm(Weight~Length1 + Length2 +Length3 + Height + Width, data = Pike)  
summary.lm(weightPerch)
``` 

The adjusted R square for pike fish is 0.9794.

### Best Models

### Best Two regressor model

```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```                      

The best regresor model is length 1 and length 3.

## Roach
```{r}
Roach = filter (Fish,Species == 'Roach')
Roach=subset(Roach,select=-Species)
weightRoach = lm(Weight~Length1 + Length2 +Length3 + Height + Width, data = Roach)  
summary.lm(weightRoach)
``` 
The adjusted r square is 0.821



### Best Models

### Best Two regressor model
```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Roach ,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```     

The best regresor model for roach is length3 and width.

## Final Summary Statements


The adjusted R square for Perch is 0.9372,the adjusted R square for Pike is 0.9794, and the adjusted R square for Roach is 0.821.How well the weight of the fish is based on the variables given.It shows that the Pike fish is the best because it has the biggest variable which is 0.9794 compared to roach and perch fish.

